Embedded Scalars: {A}n Experimental Revisit

### 2014-05-20 text/paper/paper4.tex

Forty native speakers of German took part in our study, none of which had
any prior exposure to logic or formal semantics. We excluded three
participants due to insufficient performance on controls ($\le 50\%$
correct answers).

@@

In the following, we will report the results for targets and
preference-related controls separately. After providing the
descriptive results, we present statistical analyses, which were
carried out in the following manner.  We computed log-linear models
(see SCHEEPERS 2003 ????) in two variants (by item and by participant). In
the first, the factor {\it Item} was included, and in the second
analysis, the factor {\it Participants} was included. Inclusion of
these two factors allowed us to test whether the distribution of
participants' choices was identical accros items and participants. We
report log-likelihood ratio Chi-squares ($LRCS_1$ and $LRCS_2$),
degrees of freedom ($df_1$, $df_2$) and significance levels ($p_1$ and
$p_2$). The relevant experimental factors are provided in the specific
subsections below.

\paragraph{Target conditions and positional controls.}
Performance on positional controls was overwhelmingly correct (92\% correct responses on
average) indicating that participants understood the task and were able to give
correct truth-value judgments at the adequate point in a sequence. 
In general, they were not affected by inessential features of the picture materials
or general response biases.

The judgments obtained for the four target conditions are depicted in
Figure \ref{fig:JudgmentsK2}.
%
\begin{figure}[t]
\centering

\includegraphics[width=\textwidth]{positional_answers_critical.pdf}

\caption{Positional judgments for the four target conditions. Bars
  show the total number of \emph{yes} (up) and \emph{no} judgments
  (down) against the position within a sequence. E.g., we recorded a
  total of 84 \emph{yes} judgments at the third position in the
  \as-sequence with neutral intonation, which corresponds to 84
  answers that were classified as \emph{literal} answers. Notice that
  the \as-condition has seven positions, the \es-condition only five.}
\label{fig:JudgmentsK2}
\end{figure}
%
We coded the judgments as {\it literal}, {\it global} or {\it local}
if they were as expected under one of these readings and as {\it
  error} if not. The distribution of readings thus coded is presented
in Figure~\ref{fig:JudgementPercentages}.
%
\begin{figure}[t]
\centering
\subfloat[][\as-condition]{
\begin{tikzpicture}[scale=0.75]

      \begin{axis}[ybar, 
                  enlarge x limits=0.5,
                  enlarge y limits=0.25,
                  legend style={at={(0.5,-0.15)}, anchor=north, legend columns=-1},
        ylabel={\% of answers (rounded)}, symbolic x
        coords={neutral,accented}, xtick=data, nodes
        near coords, nodes near coords align={vertical},x=65, bar
        width=3mm, ymin = 8, ymax = 73 ]

        \addplot coordinates {(neutral,73) (accented,70)};

        \addplot coordinates {(neutral,23) (accented,22)};

        \addplot coordinates {(neutral,1) (accented,2)};

        \addplot coordinates {(neutral,4) (accented,6)};

        % \addplot coordinates {(ae-ntr,83) (ae-acc,80) (ge-ntr,53)
        % (ge-acc,56)};

        % \addplot coordinates {(ae-ntr,26) (ae-acc,25) (ge-ntr,33)
        % (ge-acc,26)};

        % \addplot coordinates {(ae-ntr,1) (ae-acc,2) (ge-ntr,0)
        % (ge-acc,1)};

        % \addplot coordinates {(ae-ntr,4) (ae-acc,7) (ge-ntr,28)
        % (ge-acc,31)};

        \legend{literal, local, global, error}

% \includegraphics[width=5cm]{../pictures/paper/ReadingsAE.pdf}
\label{fig:JudgementPercentagesAE}
}
\subfloat[][\es-condition]{
\begin{tikzpicture}[scale=0.75]

  \begin{axis}[ybar, 
               enlarge x limits=0.5,
               enlarge y limits=0.25, 
               legend style={at={(0.5,-0.15)},
                 anchor=north,
                 legend columns=-1}, 
               % ylabel={\% of answers}, 
               symbolic x coords={neutral,accented}, 
               xtick=data,
               nodes near coords,
               nodes near coords align={vertical},
               x=65, bar width=3mm,
               ymin = 8, ymax = 73
               ]

    \addplot coordinates {(neutral,47) (accented,49)};

    \addplot coordinates {(neutral,29) (accented,23)};

    \addplot coordinates {(neutral,0) (accented,1)};

    \addplot coordinates {(neutral,25) (accented,27)};

    % \addplot coordinates {(ae-ntr,83) (ae-acc,80) (ge-ntr,53) (ge-acc,56)};

    % \addplot coordinates {(ae-ntr,26) (ae-acc,25) (ge-ntr,33) (ge-acc,26)};

    % \addplot coordinates {(ae-ntr,1) (ae-acc,2) (ge-ntr,0) (ge-acc,1)};

    % \addplot coordinates {(ae-ntr,4) (ae-acc,7) (ge-ntr,28) (ge-acc,31)};

    \legend{literal, local, global, error}

% \includegraphics[width=5cm]{../pictures/paper/ReadingsGE.pdf}
\label{fig:JudgementPercentagesGE}
}
\caption[Optional caption for list of figures]{Response type
  frequencies for target conditions}
\label{fig:JudgementPercentages}
\end{figure}
%
Participants mostly gave judgments indicating literal or local
readings. Judgments compatible with a global reading were seldom
observed. In the \as-conditions (see
Figure~\ref{fig:JudgementPercentagesAE}), judgments were consistent
with literal readings in 65.0\% of the trials with neutral prosody and
in 67.5\% of the trials with accented prosody. Judgments indicating
local readings were given in 22.0\% of both the neutral and accented
trials. Global readings occurred in 1.6\% of the neutral and 0.8\% of
the accented trials (corresponding to a total of 3 answers across all
trials).  In the \es-conditions (see
Figure~\ref{fig:JudgementPercentagesGE}) judgments consistent with
literal readings were given in 47.2\% and 44.7\% of the trials with
neutral and accented prosody, respectively.  Judgments indicating
local readings were given in 22.8\% of the neutral and 27.6\% of the
accented trials. Global readings were observed in 0.8\% of the trials
in both the neutral and the accented condition.  As for the number of
erroneous decisions, a discrepancy between \as-conditions and
\es-conditions was observed: In the former, participants made hardly
any errors, while in the latter, the amount of errors was considerably
larger.

Interestingly, there was considerable variation of response patterns within participants. The relative frequencies of local responses seemed to be distributed bimodally (see Figure \ref{fig:HistogramLocalReadingsK2}). We classified participants as {\it localists}, {\it globalists} or {\it inconsitent}. Table \ref{table:answer-types-as} shows how many of each type we observed. Further examination of the distribution of local readings revealed a clear pattern. The relative frequency of local judgments per participant strongly
correlated between all four conditions (all $r>.6, p<.001$). Within the non-localists, about half of the participants (41.5\% of all
participants) were consistently giving judgments that indicate literal readings. Only a minority of participants exhibited inconsistency.

\begin{figure}[t]
\centering
\subfloat[][\as-accented]{
\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_AKZ.jpg}
\label{fig:ReadingsAE}
}
\subfloat[][\as-neutral]{
\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_NTR.jpg}
\label{fig:ReadingsGE}
}

\subfloat[][\es-accented]{
\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_AKZ.jpg}
\label{fig:ReadingsAE}
}
\subfloat[][\es-neutral]{
\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_NTR.jpg}
\label{fig:ReadingsGE}
}
\caption[]{Judgments for the four target conditions}
\label{fig:HistogramLocalReadingsK2}
\end{figure}

%
\begin{table}[t]
  \centering
      \begin{tabular}{lccc}
      & \multicolumn{3}{c}{\es} \\ \cmidrule(r){2-4}
      \as & literalist & localist & incons. \\ \midrule
      literalist   & 19 & 2 & 6\\
      localist     &  0 & 7 & 0 \\
      incons. &  2 & 1 & 1\\
    \end{tabular}
    \caption{Contingency table showing the number of occurrences of
      \emph{response types} in the \as- and \es-conditions with
      neutral intonation. \emph{Literalists} are subjects who gave
      responses that were classified as either a literal response or
      an error; \emph{localist} are subjects who gave responses
      that were classified as either a 
      local response or an error. Subjects who gave at least two
      responses from different categories (literal, global, local) are
      classified as \emph{inconsistent}. (No subject's responses where
      errors exclusively and there where no \emph{globalists}, as
      defined in parallel fashion.)}
    \label{table:answer-types-as}
\end{table}
%

In order to test whether local readings occurred reliably, we compared the
number of local responses in each condition with the expected
 chance level. Local responses had to be given on the last position in
each trial where two responses were
possible. One was compatible with a local reading the other was
not. Therefore, we would expect 50\% local responses by chance. As it
turned out, local responses were given significantly more often than
50\% in all target conditions (all Bonferoni corrected p<.05). Note
that this finding cannot be explained by a general response
bias on the last position since local readings required a \emph{yes} judgment
in the \es-conditions, but a \emph{no} judgment in the \as-conditions.

In order to test whether accentuation or the quantifiers had an
influence on the distribution of readings, log-linear models 
including the factors {\it Reading}, {\it Accentuation} and 
{\it Quantifier} were computed. Since the variability within participants caught
our attention, we will below also report the interaction of {\it Participant} and {\it Reading}
in addition to effects of our experimental manipulations.

Unsurprisingly, there was an effect of \emph{Reading} ($LRCS_1=364.77,
df_1 = 3, p_1<.001, LRCS_2=364.77, df_2 = 3, p_1<.001,$) because
overall the readings were distributed inhomogeneously (see Figure
\ref{fig:JudgementPercentages}). The quantifier had an influence on the
distribution of readings as revealed by a reliable interaction of {\it
  Reading} and {\it Quantifier} ($LRCS_1=49.32, p_1<.01,LRCS_2=32.16,
p_1<.01,$). A difference in the distribution of judgment types
between participants was revealed by a reliable interaction of {\it
  Reading} and {\it Participant} ($LRCS_1=487.70, p_1<.01$).  Finally,
there was a three-way interaction of {\it Participants}, {\it
  Quantifier} and {\it Reading} ($LRCS_1, = 143.92, df_1 = 117,
p_1<.05$) which could stem from the fact that some participants were
more prone than others to make errors in the \es-conditions.

In order to find out whether the interactions just reported affected
the amount of local readings, the log-linear models were computed
again with a different coding of the readings. Here, we only
considered the amount of local readings versus all other kinds of
judgments. Judgments were coded as {\it local} and {\it other}. If the
reported interactions affected the amount of local readings, they should
have shown up again. The expected but irrelevant effect of {\it Reading} was
again significant ($LRCS_1=134.55, df_1 = 1, p_1<.001, LRCS_2=144.64,
df_2 = 1, p_1<.001$). In addition, the interaction of {\it
  Participant} and {\it Reading} ($LRCS_1=487.70, p_1<.01$) was significant. The interaction of {\it
  Quantifier} and {\it Reading} was, however, not significant ($LRCS_1=2.10,
p_1=.15,LRCS_2=.74, p_2=.39$).

The interaction of {\it Participant} and {\it Reading} indicates that
there are indeed varying preferences for local readings among German
speakers (see Table~\ref{table:answer-types-as}). The absence of the interaction
between {\it Quantifier} and {\it Reading} indicates that the type of quantifier does not affect the amount of local readings.
Based on the observed distribution of judgments, we suspected that the type of quantifier affected the
amount of literal but not local and global readings. To test
this, we also compared literal and global readings versus
other judgments in separate analyses. Comparing literal readings to
other judgments {\it Construction} and {\it Reading} were found to
interact ($LRCS_1=42.80, df= 1, p<.001; LRCS_2=22.14, df= 1,
p<.001$). Comparing global readings to other judgments no such
interaction was obeserved ($LRCS_1=1.24, df= 1, p=.29, LRCS_1=.21, df=
1, p=.65$).

\paragraph{Preference-related controls.} Participants' judgments are
depicted in Figures \ref{Fig:EC_judgments} and
\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they
were as expected under one of these readings, and as "other" if they
were not. The distributions of readings thus coded is illustrated in
Figure \ref{fig:response-type-freque-TRF}.  Overall, participants
mainly gave answers corresponding to the \lc-reading (65\%).
Moreover, this pattern was constrained by prosody. When prosody
supported a dispreferred \ec-reading, the number of \ec-decisions were
increased and vice versa.

@@

\begin{figure}[t]
\centering
\subfloat[][neutral accentuation]{
% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
\begin{tikzpicture}[scale=0.75]

      \begin{axis}[ybar, 
                  enlarge x limits=0.2,
                  enlarge y limits=0.1,
                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
                  ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,64)};

        \addplot coordinates {(1,4) (2,2) (3,26) (4,1) (5,5)};

        \legend{yes, no}

      \end{axis}
\end{tikzpicture}
% \label{fig:ReadingsAS-ntr}
}
\subfloat[][prosody cues \lc-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
\begin{tikzpicture}[scale=0.75]

      \begin{axis}[ybar, 
                  enlarge x limits=0.2,
                  enlarge y limits=0.1,
                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
                  % ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,76)};

        \addplot coordinates {(1,4) (2,0) (3,13) (4,2) (5,5)};

        % \legend{yes, no}

\end{tikzpicture}
\label{fig:ReadingsES-ntr}
}

\subfloat[][prosody cues \ec-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
\begin{tikzpicture}[scale=0.75]

      \begin{axis}[ybar, 
                  enlarge x limits=0.2,
                  enlarge y limits=0.1,
                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
                  ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,56)};

        \addplot coordinates {(1,2) (2,1) (3,33) (4,2) (5,6)};

        % \legend{yes, no}

\end{tikzpicture}
% \label{fig:ReadingsAS-acc}
}
\subfloat[][unambiguous \lc-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
\begin{tikzpicture}[scale=0.75]

      \begin{axis}[ybar, 
                  enlarge x limits=0.2,
                  enlarge y limits=0.1,
                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
                  % ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,1) (2,0) (3,0) (4,1) (5,86)};

        \addplot coordinates {(1,6) (2,0) (3,5) (4,0) (5,2)};

        % \legend{yes, no}

\end{tikzpicture}
% \label{fig:ReadingsES-acc}
}
% \includegraphics[width=\textwidth]{../pictures/paper/graph_ec.pdf}
\caption{Judgments for preference-related controls (EC
  sequence). Rounded percentages of {\it yes/no} judgments are plotted
  against the position within the trial. Each EC sequence consisted of
  five pictures, in which the critical positions for a reading were
  the third position (\emph{no} corresponded to an \ec reading) and
  the fifth position (\emph{yes} corresponded to an \lc reading).}
\label{Fig:EC_judgments}
\end{figure}

\begin{figure}[t]
\centering
\subfloat[][neutral accentuation]{
% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
\begin{tikzpicture}[scale=0.75]

      \begin{axis}[ybar, 
                  enlarge x limits=0.1,
                  enlarge y limits=0.1,
                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
                  ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,68) (4,0) (5,0) (6,1) (7,0)};

        \addplot coordinates {(1,0) (2,0) (3,5) (4,0) (5,0) (6,25) (7,2)};

        \legend{yes, no}

      \end{axis}
\end{tikzpicture}
% \label{fig:ReadingsAS-ntr}
}
\subfloat[][prosody cues \lc-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
\begin{tikzpicture}[scale=0.75]

      \begin{axis}[ybar, 
                  enlarge x limits=0.1,
                  enlarge y limits=0.1,
                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
                  % ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,79) (4,1) (5,1) (6,2) (7,1)};

        \addplot coordinates {(1,0) (2,1) (3,3) (4,0) (5,0) (6,13) (7,0)};

        % \legend{yes, no}

\end{tikzpicture}
% \label{fig:ReadingsES-ntr}
}

\subfloat[][prosody cues \ec-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
\begin{tikzpicture}[scale=0.75]

      \begin{axis}[ybar, 
                  enlarge x limits=0.1,
                  enlarge y limits=0.1,
                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
                  ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,51) (4,2) (5,1) (6,4) (7,0)};

        \addplot coordinates {(1,2) (2,0) (3,8) (4,1) (5,0) (6,30) (7,2)};

        % \legend{yes, no}

\end{tikzpicture}
% \label{fig:ReadingsAS-acc}
}
\subfloat[][unambiguous \lc-reading]{
% \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
\begin{tikzpicture}[scale=0.75]

      \begin{axis}[ybar, 
                  enlarge x limits=0.1,
                  enlarge y limits=0.1,
                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
                  % ylabel={\% of answers (rounded)}, 
                  % xlabel={position}, 
                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
                  xtick=data, 
                  nodes near coords,
                  nodes near coords align={vertical}, 
                  x=20, y=1,
                  ymin = 0, ymax = 100,
                  bar width=2mm
        ]

        \addplot coordinates {(1,0) (2,0) (3,88) (4,2) (5,0) (6,5) (7,0)};

        \addplot coordinates {(1,1) (2,0) (3,1) (4,0) (5,0) (6,3) (7,0)};

        % \legend{yes, no}

\end{tikzpicture}
% \label{fig:ReadingsES-acc}
}
% \includegraphics[width=\textwidth]{../pictures/paper/graph_lc.pdf}
\caption{Judgments for preference-related controls (LC
  sequence). Rounded percentages of {\it yes/no} judgments are plotted
  against the position within the trial. Each LC sequence consisted of
  seven pictures, in which the critical positions for a reading were
  the third position (\emph{yes} corresponded to an \lc reading) and the
  sixth position (\emph{no} corresponded to an \ec reading).}
\label{Fig:LC_judgments}
\end{figure}

% \begin{figure}
% \includegraphics[width=\textwidth]{../pictures/graph_lc.pdf}
% \end{figure}

%\begin{itemize}
%\item see Figure~\ref{fig:response-type-freque-TRF}
%\end{itemize}

>>>>

Forty native speakers of German took part in our study, none of which
had any prior exposure to logic or formal semantics. We excluded two
participant due to insufficient performance on controls ($\le 60\%$
correct answers).

@@

In the following, we will report the results for targets and
preference-related controls separately. After providing the
descriptive results, we present statistical analyses using log-linear
models (i.e., generalized linear regression for count data). To
complement the picture, we also provide a Bayesian analysis that
probes specifically into the preference relations between candidate
readings.

\paragraph{Target conditions and positional controls.}
Performance on positional controls was overwhelmingly correct (90\%
correct responses on average with a variance of 0.012) indicating that
participants understood the task and were able to give correct
truth-value judgments at the adequate point in a sequence. In
general, they were not affected by inessential features of the picture
materials or general response biases.

The answers obtained for the four target conditions are depicted in
Figure \ref{fig:JudgmentsK2}.
%
\begin{figure}[t]
\centering

\includegraphics[width=0.9\textwidth]{positional_answers_critical.pdf}

\caption{Positional judgments for the four target conditions. Bars
  show the total number of \emph{yes} (up) and \emph{no} judgments
  (down) against the position within a sequence. E.g., we recorded a
  total of 103 \emph{yes} judgments at the third position in the
  \as-sequence with neutral intonation, which corresponds to 103
  answers that were classified as \emph{literal} answers. Notice that
  the \as-condition has seven positions, the \es-condition only five.}
\label{fig:JudgmentsK2}
\end{figure}
%
We coded these answers as {\it literal}, {\it global} or {\it local}
if they were as expected under one of these readings and as {\it
  error} if not. The distribution of readings thus coded is presented
in Table~\ref{tab:CC-ContingencyTable}. The table also classifies
responses according to the position (1--3) in the experiment, i.e.,
whether it was the first, second or third time that a participant saw
the critical condition in question.
%
\begin{table}[h]
\centering

\begin{tabular}{lccccc}
  condition & position & \multicolumn{4}{c}{response type} \\ \cmidrule(r){3-6}
  && \emph{literal} & \emph{local} & \emph{global} & \emph{error} \\
  \midrule \addlinespace[0.15cm]
  \textbf{\as neutral} 
  & Pos 1 & 35 &  0 & 0 & 3 \\
  & Pos 2 & 35 &  1 & 0 & 2 \\
  & Pos 3 & 33 &  2 & 0 & 3 \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{103} &  \textbf{3} & \textbf{0} &
  \textbf{8} \\
  \addlinespace[0.25cm]
  \textbf{\as accented} 
  & Pos 1 & 33 &  2 & 1 & 2 \\
  & Pos 2 & 33 &  3 & 1 & 1 \\
  & Pos 3 & 33 &  3 & 0 & 2 \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2} &
  \textbf{5} \\
  \addlinespace[0.25cm]
  \textbf{\es neutral} 
  & Pos 1 & 26 &  5 & 0 & 7 \\
  & Pos 2 & 26 &  3 & 0 & 9 \\
  & Pos 3 & 26 &  6 & 0 & 6 \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{78} &  \textbf{14} & \textbf{0} &
  \textbf{22} \\
  \addlinespace[0.25cm]
  \textbf{\es accented} 
  & Pos 1 & 26 &  6 & 0 & 6 \\
  & Pos 2 & 24 &  5 & 0 & 9 \\
  & Pos 3 & 28 &  5 & 0 & 5 \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{78} &  \textbf{16} & \textbf{0} &
  \textbf{20}
\end{tabular}

\caption{Contingency table of classified responses for the critical
  conditions. The factor position encodes whether participants saw the
  condition in question for the first, second or third time during the
  whole experiment.}
\label{tab:CC-ContingencyTable}
\end{table}
%
The majority of answers are indicative of a literal reading (90.35\% /
86.84\% in neutral / accented \as-conditions, and 68.42\% in both
neutral / accented \es-conditions). Only two answers across all
critical conditions fall into the category indicative of global
readings. Judgements indicative of local readings, on the other hand,
are more frequent (2.63\% / 7.02\% for neutral / accented
\as-conditions, and 12.28\% / 14.04\% for neutral / accented
\es-conditions).

The number of responses that fell out of our classification scheme
differs substantially between \as- and \es-conditions. There are
7.02\% / 4.39\% unclassifiable judgements in the neutral / accented
\as-conditions, but 19.30\% / 17.54\% 'error' in the neutral /
accented \es-conditions. A look at Figure~\ref{fig:JudgmentsK2}
reveals that there is some systematicity in 'error' answers. Most
answers that we classified as 'errors' are plausibly explained as a
few random errors, a handful of mistakes resulting from confusing
buttons for \emph{true} and \emph{false} and a few 'spill-overs' where
participants gave responses one position too late. There is one
notable exception, though. A substantial number of \emph{true}
responses where given at the second position of \es-sequences (9.65\%
/ 8.77\%) which is shown in Figure~\ref{fig:exseqES2}. Although this
position in the sequence is the critical position to reveal a global
reading, the latter would be indicated by a \emph{false} response. It
appears that subjects read \es-sentences as if the non-monotonic
quantifier \emph{exactly one} was a non-monotonic \emph{at least one},
without pragmatic enrichment of \emph{some}. 16 out of the total 21
answers in this category come from 5 subjects, while the remaining 5
were single answers by 5 different subjects. \todo{subjects 1, 9, 12,
  21, 84} This suggests that at least for some subjects non-monotonic
quantifiers were problematic. \todo{how to deal with this in the future?}

We fitted generalized linear models to the contingency table data in
Table~\ref{tab:CC-ContingencyTable}, using factors \textsc{Condition}
with levels \as and \es, \textsc{Accent} with levels \emph{neutral}
and \emph{accented}, and \textsc{Position} with levels 1 through 3 to
predict the dependent factor \emph{Response} with levels
\emph{literal}, \emph{local}, and \emph{other}. The latter levels
lumps \emph{global} and \emph{error} responses together, because
otherwise we would not have enough cell counts to apply log-linear
regression. We selected the ``best'' predictor of the data by a
gradient search over hierarchical models in terms of AICs, starting
from the saturated model. The best model takes main factors
\textsc{Response} and \textsc{Condition} into account, as well as the
interaction term \textsc{Response:Condition} ($\chi^2 = 17.19$,
$df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$ of the
saturated model)). Crucially, factors \textsc{Position} and
\emph{Accent} are spurious in the best model. This suggests that
response patterns only depend on the type of the sentence, but that
there were no learning or fatigation effects and that accentuation did
not influence answer patterns significantly.

In order to test whether there is support for the postulation of local
readings, we compared the previous ``best'' model to a model that only
differs from the former in that it subsumes the level \emph{local} of
factor \textsc{Reading} under level \emph{other} as well
\citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model comparison
reveals that there is no significant improvement in explanatory power
($Pr(|\chi|) = 0.2689$) of the more complex model that includes the
level \emph{local} (df=30, residual deviance = 9.76) over the leaner
model without this level (df=32, residual deviance = 12.39,
AIC=156.63). This means that our data does not provide strong evidence
for the maintenance of belief in \emph{local} readings in our
setting. (Subsequent analysis will shed more light on this.)

\paragraph{Preference-related controls.} Positional answers for our
preference-related control conditions are shown in
Figure~\ref{Fig:TF_judgments}.
%
\begin{figure}[]
\centering

 \subfloat[][\LC-sequence]{

\includegraphics[width=0.9\textwidth]{positional_answers_TF_LC.pdf}
}

 \subfloat[][\EC-sequence]{

\includegraphics[width=0.9\textwidth]{positional_answers_TF_EC.pdf}
}

\caption{Positional answers for \lc-sequences and
  \ec-sequences. \emph{True} judgements are plotted upwards on each
  position, \emph{false} judgements downwards.}
\label{Fig:TF_judgments}
\end{figure}
%
Judgments were coded as \ec or as \lc if they were as expected under
one of these readings, and as \emph{error} if they were not. The
distributions of readings thus coded, for each position at which this
critical item occurred during the experiment, is given in
Table~\ref{tab:CC-ContingencyTable-TF}.

\begin{table}[]
\centering

\begin{tabular}{lcccc}
  condition & position & \multicolumn{3}{c}{response type} \\ \cmidrule(r){3-5}
  && \emph{LC} & \emph{EC} & \emph{error}  \\
  \midrule \addlinespace[0.15cm]
  \textbf{\lc neutral} 
  & Pos 1 & 27 &  7  & 4 \\
  & Pos 2 & 23 &  11 & 4 \\
  & Pos 3 & 26 &  9  & 3 \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{103} &  \textbf{3} & \textbf{0}  \\
  \addlinespace[0.25cm]
  \textbf{\lc with \lc cue} 
  & Pos 1 & 26 &  6 & 5  \\
  & Pos 2 & 31 &  5 & 2  \\
  & Pos 3 & 33 &  3 & 2  \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
  \addlinespace[0.25cm]
  \textbf{\lc with \ec cue} 
  & Pos 1 & 14 &  18 & 3  \\
  & Pos 2 & 16 &  16 & 1  \\
  & Pos 3 & 14 &  17 & 5  \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
  \addlinespace[0.25cm]
  \textbf{\ec neutral} 
  & Pos 1 & 22 &  6 & 10  \\
  & Pos 2 & 28 &  6 & 4  \\
  & Pos 3 & 28 &  8 & 2  \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
  \addlinespace[0.25cm]
  \textbf{\ec with \lc cue} 
  & Pos 1 & 30 &  5 & 3  \\
  & Pos 2 & 32 &  5 & 1  \\
  & Pos 3 & 30 &  3 & 2  \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
  \addlinespace[0.25cm]
  \textbf{\ec with \ec cue} 
  & Pos 1 & 19 &  10 & 9  \\
  & Pos 2 & 19 &  7  & 12  \\
  & Pos 3 & 19 &  7  & 12  \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
\end{tabular}

\caption{Contingency table of classified responses for the
  preference-related controls. As before, the factor position encodes
  whether participants saw the condition in question for the first,
  second or third time during the whole experiment.}
\label{tab:CC-ContingencyTable-TF}
\end{table}

\bigskip

Judgments were
coded as \ec or as \lc if they were as expected under one of these
readings, and as "other" if they were not. The distributions of
readings thus coded is illustrated in Figure
\ref{fig:response-type-freque-TRF}.  Overall, participants mainly gave
answers corresponding to the \lc-reading (65\%).  Moreover, this
pattern was constrained by prosody. When prosody supported a
dispreferred \ec-reading, the number of \ec-decisions were increased
and vice versa.

@@
